\documentclass{beamer}

\usepackage[utf8]{inputenc}

\title{How the Standard for Public Code can help you collaborate over time and space}
%\subtitle{Database usage for the real world for flexibility and scale}
\author{Eric Herman}
\institute{Foundation for Public Code}
\date{2021-02-10}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{hello, world}
Eric Herman\newline
Lead codebase steward\newline
Foundation for Public Code
\begin{itemize}
\item Foundation for Public Code, 2019-present
\item MariaDB Foundation Board of Directors 2015-present
\item Booking.com 2010-2019
\item MySQL 2004-2010
\item Product Sight 2000-2004
\item Open Hardware designer, presented at FOSDEM 2020
\item Other contributions here and there
\item ... including in Perl interpreter, GNU binutils
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{What is Public Code?}
\huge{ FOSS developed by public organizations }\newline
\huge{ + public policy }\newline
\huge{ = Public Code }\newline\newline
\textbf{Essential public infrastructure is sometimes software}
\end{frame}

\begin{frame}
\frametitle{Why do we need the Standard?}
`Digital transformation of the public sector'\newline\newline
Expectations and requirements for public infra tend to be higher
\begin{itemize}
\item Transparency
\item Reliability
\item Accountability
\item Predictability
\item Sustainability
\item Sovereignty\newline
\end{itemize}
May seem too much to ask of a small public organization.\newline
There are many organizations with similar needs.\newline

We are achieving this together, collaboratively.
\end{frame}

\begin{frame}
\frametitle{The Standard for Public Code}

\textbf{https://standard.publiccode.net/}\newline

Describes the minimum requirements to collaboratively create reliable, reusable
public software infrastructure.\newline

\begin{itemize}
\item Criteria are list of requirements and practices
\item Code and community
\begin{itemize}
\item Familiar, common
\item Most practices your team is likely already doing
\item Most of the rest you probably wish you were
\end{itemize}
\item Role oriented guidance
\begin{itemize}
\item Policy Makers
\item Management
\item Developers and designers
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Applying the Standard}
Public administrations have the growing understanding software is a process,
not a product.\newline

The Standard facilitates the building and enhancement of public
purpose software by public administrations.\newline

\begin{itemize}
\item Procurement in increments
\item Increase control
\item Reduce risk
\item Reduce cost
\item Increase effectiveness\newline
\end{itemize}
\textbf{Investing in collaboration} does not cost, it \textbf{pays!}
\end{frame}

\begin{frame}
\frametitle{Thank you}
I invite you to review the Standard for Public Code and participate.\newline
\begin{itemize}
\item eric@publiccode.net
\item github.com/ericherman
\item twitter.com/Eric\_Herman
\end{itemize}
\end{frame}

\end{document}
